Bird beak's elaboration and innovation

### 2022-09-09 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

>>>>

## Get the variance for each level
variance_per_levels <- MCMCglmm.variance(shapespace_allbirds_lvl_superorder_order)
## Rename the columns
colnames(variance_per_levels) <- c(levels(shapespace$level1)[-1], levels(shapespace$level2)[-1], "phylogeny", "residuals")

## Plot the results
pdf(file = "../Manuscript/Figures/variance_per_levels_whole_tree.pdf")
par(mar = c(5,10,2,2))
boxplot(variance_per_levels, horizontal = TRUE, las = 1, main = "Scaled variance by term", xlab = "Scaled variance (sum of each VCV)")
dev.off()
